---
title: "Crowdsourcing Public Value"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

This exercise was designed as part of an ongoing collaboration between INCAE Business School and Contraloría General de la República de Costa Rica.  It presents to the student with a concrete data challenge:  As a result of an open government policy, the Costa Rican Republic has made its procurement data publicly available.  The student is presented with some context information, a brief introduction to a basic framework on public value creation, a set of questions to help as a guide to understand the underlying technical infrastructure allowing this ability, and finally with a subset of data (over a hundred lines) of public data.   The dataset contains five years of information on information technology that was acquired or rented using public funds.  The challenge is to propose to public officials concrete ways to add value based on their analysis of these data.

## Objectives
* Test and develop the basic skills for data management and exploratory data analysis
* Recognize the benefits and drawbacks of being a power user as opposed to information consumers from predefined searches in a Business Intelligence platform
* Recognize the challenges for Open Government Initiatives in terms of design, implementation and adoption

Extra-Curricular Objectives
* Students papers, insights and discussion will contribute to the advancement of current efforts to promote a data-driven discussion about open data in general and procurement in particular, in Costa Rica and beyond.
Assumptions
The student has succesfully completed a Quantitative Methods course and therefore understands the following subjects:
* Utilizes visualization techniques (Tableau, Rstudio) for an exploratory data analysis
* Can perform a linear regression against dummy variables to identify significant relationships.
* Can perform a logistic regression to evaluate proportions when using categorical variables.

The student has critical thinking and written communication skills, necessary for:
* Identify evidence (can recognize the difference between working and critical assumptions provided the lack of data)
* Evaluate Arguments
* Develop well-constructed conclusions.


## Contextual Information

Costa Rica has been considered one of the 20th more robust Democracies in the world (The EIU, 2018).  But as most of them, it is facing important challenges as citizens demand more transparency, efficiency and public participation. 

According to the World Bank, “Open government is built on the idea that citizens have the right to access government information, to actively participate in government decisions that affect their livelihoods, and to hold government officials and/or service providers to account when they fail to govern properly (World Bank Group, 2017)”.

Public procurement, therefore, is a key element in any Open Data initiative, but in this regard, the country is lacking citizen involvement, even though, data has been available through Contraloría General de la República.  A recent assessment stated:

“The absence of an institutionalized mechanism that allows for the participation of civil society in the public procurement system. In general terms, there is little citizen participation and almost no supervision from civil society over the contracting processes, and little consideration of public opinion and of interested parties, both in the design stages and in the contractual execution stages.” (Gobierno de la República de Costa Rica, 2019)

Costa Rica is a member of the Open Government Partnership since 2012 and its current action plan list 12 commitments to be accomplished by the year 2019: 
“Poner a disposición de la ciudadanía los datos generados por el SICOP en formato abierto, neutral e interoperable, siguiendo los estándares de contratación abierta de Open Contracting Partnership”. (Gobierno de la República de Costa Rica, 2019)

Data savvy MBA students, and future business leaders, can and should play a role in Public or Private Value creation and this exercise provide an opportunity to test knowledge, ingenuity and creativity.


## A Gentle Introduction to Public Value creation

Public value can be described in terms of six general types that capture the range of possible results of government in the ways of interest… (Harrison et al., 2011)

* Financial – impacts on current or future income, asset values, liabilities, entitlements, or other aspects of wealth or risks to any of the above. 
* Political – impacts on a person’s or group’s influence on government actions or policy, on their role in political affairs, influence in political parties or prospects for public office. 
* Social – impacts on family or community relationships, social mobility, status, and identity. 
* Strategic – impacts on person’s or group's economic or political advantage or opportunities, goals, and resources for innovation or planning. 
* Ideological – impacts on beliefs, moral or ethical commitments, alignment of government actions or policies or social outcomes with beliefs, or moral or ethical positions. 
* Stewardship – impacts on the public’s view of government officials as faithful stewards or guardians of the value of the government in terms of public trust, integrity, and legitimacy. 

...Actions to effect transparency, participation, and collaboration belong within this group of value generators. Taken as a whole, the set of value generators consists of (Harrison et al., 2011): 

* efficiency – obtaining increased outputs or goal attainment with the same resources or obtaining the same outputs or goals with lower resource consumption. 
* effectiveness – increasing the quality of the desired outcome. 
* intrinsic enhancements – changing the environment or circumstances of a stakeholder in ways that are valued for their own sake. 
* transparency – access to information about the actions of government officials or operation of government programs that enhances accountability or influence on government. 
* participation – frequency and intensity of direct involvement in decision making about or operation of government programs or in selection of or actions of officials. 
* collaboration – frequency or duration of activities in which more than one set of stakeholders share responsibility or authority for decisions about operation, policies, or actions of government. 

```{r code=readLines("Import Files.R")}
```

```{r, code=readLines("Setup.R")}
```

<<<<<<< HEAD
```{r, eval=F, echo=T}
####Load data####
spanish_stop_words <- readRDS("spanish_stop_words.Rds")
reduccion <- SIACSICOP1519
reduccion$DESC_BIEN_SERVICIO <- tolower(reduccion$DESC_BIEN_SERVICIO)
#### Generación de Corpus ####
corpus <- reduccion %>%
  mutate(text = gsub(x = DESC_BIEN_SERVICIO, pattern = "[0-9]+|[[:punct:]]|\\(.*\\)", replacement = "")) %>%
  select(text) %>%
  mutate(id = as.character(row_number())) %>%
  unnest_tokens(word, text) %>%
  anti_join(spanish_stop_words) 

#### Cuenta de palabras ####
count_corpus <- corpus %>%
  count(word, sort = TRUE) 

####Counting words  among sections ####
word_pairs <- corpus  %>%
  pairwise_count(word, id, sort = TRUE)
word_pairs
#### Correlate among sections ####
word_1 ="caja"
word_cors <- corpus %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(word, id, sort = TRUE) %>%
  filter(item1 == word_1)
#### Correlate Specific terms ####
word_cors %>%
  filter(item1 %in% c(word_1)) %>%
  group_by(item1) %>%
  top_n(6) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()


Check <- reduccion[grepl(word_1, reduccion$DESC_BIEN_SERVICIO, perl = TRUE),] # check words in database
Check  <- Check %>% select(DESC_BIEN_SERVICIO, tech)

```

=======
>>>>>>> a8df5f1a89851c69c670a4869150838737036632

## Text-Mining

###Categorización de palabras

El proceso de categorización de palabras fue el siguiente:

<<<<<<< HEAD
###
* El proceso inicia por desagregar cada palabra de una descripción de servicio en palabras individuales con un número correlativo que las identifica.

* Posteriormente se realiza un trabajo de clasificación para cada palabra. Se relacionan bases de datos de términos que son reconocidos como palabras asociadas a tecnología que [No] se eliminan de la base datos, otras que [Si] se eliminan y otras que [Talvez] se pueden eliminar pero no se tiene un criterio definitivo aún. Otras palabras se clasifican como numéricas o palabras genéricas del idioma castellano. 

* Además, se identifican palabras que se encuentran en una base de datos de provincias, cantones y distritos. Estas palabras carecen de sentido para el análisis y se tratan como lugares. 

* Ya con la clasificación de las palabras que componen una descripción del bien o servicio que se desea adquirir. Para cada línea se genera el porcentaje de palabras como Tecnológico, No Tecnológico y Otros.  

```{r}
head(Stats)   
```



=======
>>>>>>> a8df5f1a89851c69c670a4869150838737036632
